### 2024-01-12 README.Rmd
fix readme list

```{bash eval=FALSE}
arr=(192 191 190 189 188 187 186 185 184 183 182 181 180 179 178 177 176 175 174 173 172 171 170 87 86 85 84 83 82 81 80 79 78 77 76 75 74 73 72 65 64 63 62 61 60 59 58 57 55 54 53 52 51 50 49 48 47 46 44 43 42 41 40 39 37 35 33 32 31 30 28 25 23 21 20 19 18 17 16 15 13 10);
for id in ${arr[@]}; do         
  # url="http://localhost:8080/api/projects/${id}/export?exportType=JSON&download_all_tasks=true";
  url="http://localhost:8080/api/projects/${id}/export?exportType=JSON";
  curl -X GET "$url" -H 'Authorization: Token 3135fdd1f4a5b9b3630b69011ec4d70e7800c41d'\
    -o "files/outputs/ls/output_file_$id.json";
done
```

>>>>

```{bash eval=FALSE}
arr=(192 191 190 189 188 187 186 185 184 183 182 181 180 179 178 177 176 175 174 173 172 171 170 86 85 84 83 82 81 80 79 78 77 76 75 74 73 72 65 64 63 62 61 60 59 58 57 55 54 53 52 51 50 49 48 47 46 44 43 42 41 40 39 37 35 33 32 31 30 28 25 23 21 20 19 18 17 16 15 13 10);
for id in ${arr[@]}; do         
  # url="http://localhost:8080/api/projects/${id}/export?exportType=JSON&download_all_tasks=true";
  url="http://localhost:8080/api/projects/${id}/export?exportType=JSON";
  curl -X GET "$url" -H 'Authorization: Token 3135fdd1f4a5b9b3630b69011ec4d70e7800c41d'\
    -o "files/outputs/ls/output_file_$id.json";
done
```
